\documentclass[11pt,a4paper]{article}

% --- Geometry & Layout ---
\usepackage[top=1.6cm, bottom=1.6cm, left=2.2cm, right=2.2cm]{geometry}
\usepackage{parskip}
\setlength{\parskip}{5.5pt}
\setlength{\parindent}{0pt}
\pagestyle{empty}

% --- Fonts ---
\usepackage{fontspec}
\setmainfont{Helvetica Neue}[
  UprightFont = *,
  BoldFont = * Bold,
  ItalicFont = * Italic,
  BoldItalicFont = * Bold Italic
]

% --- Color & Hyperlinks ---
\usepackage{xcolor}
\definecolor{accent}{HTML}{1A1A2E}
\definecolor{subtlegray}{HTML}{555555}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=accent,
  linkcolor=accent,
  pdfauthor={Florian Ziesche},
  pdftitle={Cover Letter – Index Ventures Applied AI Investor}
}

% --- Micro-typography ---
\usepackage{microtype}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=1.2em, itemsep=0pt, parsep=0pt, topsep=2pt}

\begin{document}

% --- Header ---
{\fontsize{18}{20}\selectfont\bfseries Florian Ziesche}\hfill{\small\color{subtlegray}New York City}

\vspace{-2pt}
{\small
\href{mailto:florian@ziesche.co}{florian@ziesche.co}\enspace·\enspace 347.740.1465\enspace·\enspace
\href{https://www.linkedin.com/in/florian-ziesche-352b7249/}{LinkedIn}\enspace·\enspace
\href{https://github.com/fziescheus-alt}{GitHub}}

\vspace{4pt}
{\color{subtlegray}\hrule height 0.4pt}
\vspace{6pt}

% --- Date & Addressee ---
{\small\color{subtlegray} February 2026}

\vspace{1pt}
{\bfseries Martin Mignot \& the Index Ventures Team}\\
{\small Applied AI Investor – New York}

\vspace{6pt}
% --- Opening ---

When you backed Personio in Munich, you bet on a first-time founder in his twenties building enterprise software in a market that most US investors couldn't locate on a map. That pattern—European builder, global ambition, product-led execution—is one I know intimately, because I lived it. As CEO of 36ZERO Vision, I built a cloud computer-vision platform from a TUM research lab into production deployments at BMW, Siemens, and Bosch, raising \texteuro5.5M along the way. I'm writing because the Applied AI Investor role is the rare position where everything I've built converges: operator depth in applied AI, a European founder's instinct, and the product lens your job description calls for—now based ten minutes from your West Village office.

% --- Applied AI Operator Section ---
\textbf{I didn't study applied AI. I shipped it.}\enspace At 36ZERO, I was simultaneously CEO \emph{and} product manager: scoping LLM-based features, defining retrieval-augmented generation pipelines, and sitting across the table from Siemens procurement asking why our hallucination rate was below 0.2\%. In one year I grew total contract value 200\%+ to \$1.025M, signing enterprise customers who required production-grade AI—not demos. That meant building agentic workflows, multi-agent architectures, and feedback loops that improved with every deployment—exactly the AI-and-automation flywheel you've described as what excites you most about the next decade.

I still build. My open-source \href{https://github.com/fziescheus-alt/CNC_Planner_PRO}{\textbf{CNC\_Planner\_PRO}} applies ML to manufacturing cost estimation—vertical AI for an industry that barely uses spreadsheets yet. My \href{https://github.com/fziescheus-alt}{\textbf{Exec-Research-Factory}} produces decision-grade research with traceable evidence chains, the kind of rigor I'd bring to every deal memo. These aren't weekend toys; they reflect a conviction that applied AI's biggest returns come from embedding intelligence in domains most technologists ignore.

% --- European Bridge Section ---
\textbf{The transatlantic lens Index needs.}\enspace You opened the New York office in 2022 to partner with globally minded founders ``whether they start in Europe or North America.'' I \emph{am} that founder. I know what it's like to pitch a Bavarian Mittelstand CTO in German at 9\,a.m.\ and a New York growth-equity partner in English by 3\,p.m. I understand European compliance culture, the grant-heavy early funding landscape, and why a Munich startup might choose London over the Bay Area—context most US-based candidates simply cannot offer. Through VC Lab (Decile Group, Cohort 6), I'm currently building Ainary Ventures, sharpening the exact sourcing, diligence, and portfolio-support skills this apprenticeship is designed to teach.

% --- Why Index ---
\textbf{Why Index, specifically.}\enspace You back Algolia, Figma, Notion, Deliveroo—companies where product craft \emph{is} the moat. That resonates deeply with someone who has spent years obsessing over how AI meets the end user, not just the model. Your culture of ``no sharp elbows'' and treating venture as a craft is a philosophy I share: the best investor-founder relationships are built on genuine empathy and relentless curiosity, not transactional access.

I'd welcome the chance to show you how an operator who has built, sold, and scaled applied AI—across two continents—can help Index win the next generation of AI-native companies.

\vspace{10pt}

Florian Ziesche

\end{document}
