\documentclass[a4paper,11pt]{article}

\usepackage{fontspec}
\setmainfont{Helvetica Neue}[BoldFont=Helvetica Neue Bold, ItalicFont=Helvetica Neue Italic]
\usepackage[top=28mm, bottom=34mm, left=28mm, right=28mm]{geometry}
\usepackage{parskip}
\setlength{\parskip}{8pt}
\setlength{\parindent}{0pt}

\usepackage{xcolor}
\definecolor{primary}{HTML}{2563EB}
\definecolor{darkbg}{HTML}{0A0F1E}
\definecolor{darkblue}{HTML}{1E3A5F}
\definecolor{bodytext}{HTML}{374151}
\definecolor{heading}{HTML}{111827}
\definecolor{subtitle}{HTML}{64748B}
\definecolor{lightgray}{HTML}{F8F9FA}
\definecolor{border}{HTML}{E5E7EB}
\definecolor{accent}{HTML}{93C5FD}
\definecolor{lightondark}{HTML}{D1D5DB}
\definecolor{darkred}{HTML}{B91C1C}
\definecolor{darkgreen}{HTML}{15803D}
\definecolor{darkyellow}{HTML}{92400E}
\definecolor{lightblue}{HTML}{F0F4FF}
\definecolor{lightred}{HTML}{FEF2F2}
\definecolor{lightgreen}{HTML}{F0FDF4}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0.4pt}
\fancyfoot[L]{\footnotesize\color{subtitle}\textls[50]{36ZERO VISION · STRATEGIC REPORT}}
\fancyfoot[R]{\footnotesize\color{subtitle}\thepage}

\usepackage{titlesec}
\titleformat{\section}{\needspace{6\baselineskip}\fontsize{24}{28}\selectfont\bfseries\color{heading}}{}{0em}{}[\vspace{-2pt}]
\titleformat{\subsection}{\needspace{4\baselineskip}\fontsize{14}{18}\selectfont\bfseries\color{heading}}{}{0em}{}
\titlespacing*{\section}{0pt}{0pt}{4pt}
\titlespacing*{\subsection}{0pt}{16pt}{6pt}

\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=1.2em, itemsep=2pt, parsep=0pt, topsep=4pt}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=primary, urlcolor=primary}
\usepackage{tikz}
\usetikzlibrary{calc,positioning,shapes.geometric}
\usepackage{tcolorbox}
\tcbuselibrary{skins,breakable}
\usepackage{microtype}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{float}
\usepackage{needspace}
\usepackage{multicol}
\usepackage{amssymb}

\usepackage{polyglossia}
\setdefaultlanguage{english}

\tolerance=2000
\emergencystretch=15pt
\hbadness=2000
\widowpenalty=10000
\clubpenalty=10000
\brokenpenalty=10000

\newcommand{\ssubtitle}[1]{\par\textcolor{subtitle}{\fontsize{12}{16}\selectfont #1}\par\vspace{2pt}\textcolor{border}{\rule{\linewidth}{0.4pt}}\vspace{12pt}}

\newtcolorbox{highlightbox}{colback=lightblue, colframe=primary, leftrule=3pt, rightrule=0pt, toprule=0pt, bottomrule=0pt, arc=0pt, outer arc=4pt, boxsep=4pt, left=12pt, right=12pt, top=8pt, bottom=8pt, fontupper=\fontsize{11}{15}\selectfont\color{darkblue}}
\newtcolorbox{darkhighlight}{colback=darkbg, colframe=primary, leftrule=3pt, rightrule=0pt, toprule=0pt, bottomrule=0pt, arc=0pt, outer arc=4pt, boxsep=4pt, left=12pt, right=12pt, top=8pt, bottom=8pt, fontupper=\fontsize{11}{15}\selectfont\color{white}}

\newcommand{\statcard}[2]{\begin{tikzpicture}\node[fill=lightgray, rounded corners=4pt, minimum width=4.4cm, minimum height=2.2cm, inner sep=6pt, align=center, text width=4cm] {{\fontsize{20}{24}\selectfont\bfseries\color{primary}#1}\\[3pt]{\fontsize{8}{10}\selectfont\color{subtitle}\MakeUppercase{#2}}};\end{tikzpicture}}
\newcommand{\statcardred}[2]{\begin{tikzpicture}\node[fill=lightred, rounded corners=4pt, minimum width=4.4cm, minimum height=2.2cm, inner sep=6pt, align=center, text width=4cm] {{\fontsize{20}{24}\selectfont\bfseries\color{darkred}#1}\\[3pt]{\fontsize{8}{10}\selectfont\color{subtitle}\MakeUppercase{#2}}};\end{tikzpicture}}
\newcommand{\statcardgreen}[2]{\begin{tikzpicture}\node[fill=lightgreen, rounded corners=4pt, minimum width=4.4cm, minimum height=2.2cm, inner sep=6pt, align=center, text width=4cm] {{\fontsize{20}{24}\selectfont\bfseries\color{darkgreen}#1}\\[3pt]{\fontsize{8}{10}\selectfont\color{subtitle}\MakeUppercase{#2}}};\end{tikzpicture}}
\newcommand{\arrow}{$\rightarrow$}
\newcommand{\ruleitem}[3]{\needspace{3\baselineskip}\noindent\begin{minipage}[t]{0.07\linewidth}{\fontsize{16}{20}\selectfont\bfseries\color{primary}#1}\end{minipage}\begin{minipage}[t]{0.91\linewidth}{\fontsize{11}{14}\selectfont\bfseries\color{heading}#2}\\[2pt]{\fontsize{10.5}{14}\selectfont\color{bodytext}#3}\end{minipage}\par\vspace{8pt}}
\newcommand{\darkruleitem}[3]{\noindent\begin{minipage}[t]{0.07\linewidth}{\fontsize{16}{20}\selectfont\bfseries\color{accent}#1}\end{minipage}\begin{minipage}[t]{0.91\linewidth}{\fontsize{11}{14}\selectfont\bfseries\color{white}#2}\\[2pt]{\fontsize{10.5}{14}\selectfont\color{lightondark}#3}\end{minipage}\par\vspace{6pt}}

\renewcommand{\normalsize}{\fontsize{11}{15}\selectfont}
\color{bodytext}

\begin{document}

\thispagestyle{empty}
\begin{tikzpicture}[remember picture, overlay]
  \fill[darkbg] (current page.south west) rectangle (current page.north east);
  \node[anchor=north west, text width=12cm] at ($(current page.north west)+(3cm,-4cm)$) {
    {\fontsize{11}{14}\selectfont\color{accent}\textls[200]{STRATEGIC RESEARCH REPORT}}\\[24pt]
    {\color{primary}\rule{50pt}{2.5pt}}\\[32pt]
    {\fontsize{38}{44}\selectfont\bfseries\color{white}From Inspection to\\Autonomous Quality}\\[18pt]
    {\fontsize{16}{22}\selectfont\color{lightondark}How 36ZERO Vision becomes the operating system for manufacturing quality --- and why the timing is now.}
  };
  \node[anchor=south west] at ($(current page.south west)+(3cm,5.5cm)$) {
    \begin{tabular}{@{}l@{\hspace{36pt}}l@{\hspace{36pt}}l@{}}
      {\fontsize{30}{34}\selectfont\bfseries\color{accent}15--20\%} & {\fontsize{30}{34}\selectfont\bfseries\color{accent}80\%} & {\fontsize{30}{34}\selectfont\bfseries\color{accent}\$41.7B} \\[2pt]
      {\fontsize{9}{11}\selectfont\color{lightondark}\MakeUppercase{Cost of Poor Quality (\% Rev.)}} & {\fontsize{9}{11}\selectfont\color{lightondark}\MakeUppercase{Manual Detection Rate}} & {\fontsize{9}{11}\selectfont\color{lightondark}\MakeUppercase{Market Size 2030}}
    \end{tabular}
  };
  \node[anchor=south west] at ($(current page.south west)+(3cm,3cm)$) {
    {\fontsize{14}{18}\selectfont\color{accent}Florian Ziesche}\\[3pt]
    {\fontsize{11}{14}\selectfont\color{lightondark}Version 2.0 · February 2026 · Confidential}
  };
\end{tikzpicture}
\clearpage

\section{Executive Summary}
\ssubtitle{The opportunity is bigger than the current vision.}

36ZERO Vision has a strong technological foundation: data-efficient AI (5--20 images), customers like Siemens, Bosch, and LEONI, partnerships with SAP and Bosch Rexroth. But ``AI Visual Inspection'' is a feature, not a company. The vision must grow.

\begin{highlightbox}
The core insight: Inspection is only the data layer. The real value lies above it --- in diagnosis, knowledge building, and autonomous correction.
\end{highlightbox}

\subsection{The Evolution --- Three Stages Beyond Today}

\begin{darkhighlight}
\darkruleitem{\arrow}{Prerequisite: Vision --- ``What is broken?''}{Visual defect detection. Where 36ZERO stands today. Fast, reliable, data-efficient.}
\darkruleitem{1}{Memory --- ``Why is it broken?''}{Knowledge base + ERP data. Root cause analysis, industry knowledge, collective intelligence.}
\darkruleitem{2}{Autonomous Quality --- ``How do we prevent it?''}{Agentic AI. Agent detects \arrow{} diagnoses \arrow{} corrects. Self-Improving: learns from every part.}
\darkruleitem{3}{Manufacturing Quality OS --- ``The Platform''}{Predictive Quality, Cross-Plant Benchmarking, Manufacturing GPT, Quality-as-a-Service.}
\end{darkhighlight}

\textbf{Each stage triples customer value and addressable market.} Competitors remain stuck at the prerequisite.

\vspace{6pt}
\noindent\begin{minipage}[t]{0.32\linewidth}\centering\statcard{\$30B}{AI Inspection Market}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcard{3--5x}{Customer Value per Stage}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcard{0}{Closed-Loop Competitors}\end{minipage}

\clearpage
\section{The Customer Problem}
\ssubtitle{Why visual quality control fails today --- and what it costs.}

Manual inspection is the foundation of quality control. And it's crumbling:

\vspace{6pt}
\noindent\begin{minipage}[t]{0.32\linewidth}\centering\statcard{80--85\%}{Inspector Detection Rate}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcard{up to 40\%}{False Positive Rate}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcard{15--20\%}{COPQ (\% of Revenue)}\end{minipage}
\vspace{6pt}

\subsection{The Five Biggest Pain Points}

\begin{minipage}[t]{0.48\linewidth}
\textbf{\color{darkred}Fatigue \& Inconsistency}\\
{\small Inspectors achieve max.\ 80--85\% detection. After 2h, attention drops significantly. \textit{Source: Pharmaceutical Technology}}

\vspace{6pt}
\textbf{\color{darkred}Knowledge Drain}\\
{\small 13--20M workers retiring by 2036. 30 years of expertise disappear irreversibly.}

\vspace{6pt}
\textbf{\color{darkred}Scaling Problem}\\
{\small More production = more inspectors. Linear costs, no economies of scale.}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\linewidth}
\textbf{\color{darkred}Scrap \& Rework}\\
{\small COPQ: 8--15\% of revenue in Automotive, Aerospace, Medtech. Up to 20\% for typical manufacturers. \textit{Source: ASQ}}

\vspace{6pt}
\textbf{\color{darkred}Recall Costs}\\
{\small 28M vehicles recalled in USA 2024 (445 campaigns). Single recall: \$97--194M. \textit{Source: NHTSA, GM}}
\end{minipage}

\subsection{How 36ZERO Solves These Problems}

\begin{minipage}[t]{0.48\linewidth}
\textbf{\color{darkgreen}24/7 Consistency}\\
{\small AI doesn't fatigue. Every part, every shift, around the clock.}

\vspace{6pt}
\textbf{\color{darkgreen}Digitize Knowledge}\\
{\small 20 images \arrow{} 30 years of expertise as an AI model.}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\linewidth}
\textbf{\color{darkgreen}Early Detection}\\
{\small Catch defects at the source. Costs multiply 10x per stage.}

\vspace{6pt}
\textbf{\color{darkgreen}Data-Efficient}\\
{\small 5--20 images instead of thousands. Perfect for rare defects.}
\end{minipage}

\clearpage
\section{ROI: Real Numbers}
\ssubtitle{What AI-based inspection delivers in practice --- documented results.}

\begin{tabularx}{\linewidth}{@{}l l X@{}}
\toprule
\textbf{Industry} & \textbf{Problem} & \textbf{Result} \\
\midrule
Medical Devices & 12,000 False Rejects/Week & Reduced to 246 \arrow{} \textbf{\$18M/Year saved} \\
Semiconductor & 60 Manual Inspectors & Reduced to 24 \arrow{} \textbf{\$691K/Year} \\
Semiconductor & +0.1\% Yield & \textbf{+\$75M/Year} (TSMC scale) \\
Automotive & Closed-Loop QC & \textbf{--23\% Defects}, €89K avoided \\
\bottomrule
\end{tabularx}

\subsection{Cost Comparison: Manual vs.\ 36ZERO}

\begin{tabularx}{\linewidth}{@{}l X X@{}}
\toprule
\textbf{Cost Factor} & \textbf{Manual} & \textbf{36ZERO} \\
\midrule
Personnel (3-Shift) & €150--250K/Year per Line & €0 (AI replaces) \\
Detection Rate & 80--85\% (declining) & {>}95\% (constant, 24/7) \\
False Positives & Up to 40\% (rule-based) & {<}5\% (data-driven) \\
New Product Setup & Weeks & Hours (5--20 images) \\
Scaling & Linear (more = costlier) & Marginal cost near 0 \\
\bottomrule
\end{tabularx}

\subsection{The ROI Multiplier}

\vspace{4pt}
\noindent\begin{minipage}[t]{0.32\linewidth}\centering\statcard{1x}{Detection in Production}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcard{10x}{Detection at Assembly}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcard{100x}{Detection at Customer}\end{minipage}

\begin{highlightbox}
The earlier in the process a defect is caught, the more dramatic the savings. 36ZERO's inline inspection detects defects at the point of origin.
\end{highlightbox}

\clearpage
\section{Agentic Quality}
\ssubtitle{Autonomous agents that don't just find defects --- they fix them.}

Agentic AI is the hottest trend in industrial software. AI agents that act autonomously --- without human intervention.

\subsection{The Concrete Workflow}

\ruleitem{01}{Detect}{Camera identifies a crack on a brake disc. This is what 36ZERO does today --- fast, reliable, with 5 training images.}
\ruleitem{02}{Diagnose}{System queries knowledge base: ``Crack type 3B = typical for spindle temperature {>}180°C.'' Root cause identified.}
\ruleitem{03}{Prescribe}{Automatic recommendation: Calibrate spindle, replace tool, inspect next 50 parts.}
\ruleitem{04}{Act}{Via Bosch ctrlX: Agent sends correction command directly to PLC. Machine parameters adjusted. No operator needed.}

\subsection{Why Now?}

\begin{tabularx}{\linewidth}{@{}l X@{}}
\toprule
\textbf{Enabler} & \textbf{Status 2026} \\
\midrule
Agentic AI Frameworks & 40\% Enterprise Apps integrate AI Agents by 2026 (Gartner) \\
PLC Connectivity & Bosch ctrlX = open platform, API-driven \\
Edge Computing & NVIDIA Jetson/Orin: 275 TOPS on-premise \\
Regulation & EU GMP Annex 22 creates framework for AI in Pharma \\
\bottomrule
\end{tabularx}

\begin{darkhighlight}
Detect \arrow{} Diagnose \arrow{} Prescribe \arrow{} Act. No single competitor offers this complete loop. The white space is real and measurable.
\end{darkhighlight}

\clearpage
\section{Self-Improving AI}
\ssubtitle{Already reality today --- and the key to the Autonomous Quality loop.}

36ZERO uses self-improving principles today: data-efficient training with 5--20 images, active learning from user feedback. Next step: full automation.

\subsection{Three Dimensions of Self-Improvement}

\ruleitem{01}{Self-Training: AI Learns From Every Part}{Every inspected part is a training data point. Active Learning: The system specifically requests labels for edge cases. Detection rate improves with every shift.}
\ruleitem{02}{Self-Calibrating: AI Controls the Environment}{Actively controls lighting (brightness, angle, wavelength). Cameras self-calibrate during vibrations or temperature changes.}
\ruleitem{03}{Self-Adapting: New Product? No Problem.}{Product changes traditionally require weeks. Self-Improving AI recognizes the new baseline and begins defect detection immediately.}

\vspace{8pt}
\noindent\begin{minipage}[t]{0.32\linewidth}\centering\statcard{0}{Programmers Needed}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcard{1 Click}{User Confirms}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcard{99\%}{Defect Reduction (WEF)}\end{minipage}

\begin{darkhighlight}
The Flywheel Effect: More inspections \arrow{} more data \arrow{} better model \arrow{} fewer defects \arrow{} more trust \arrow{} more inspections. Traditional systems degrade. Self-Improving AI gets better over time.
\end{darkhighlight}

\clearpage
\section{ERP Integration}
\ssubtitle{The fastest path to more customer value --- and the strongest lock-in.}

The most acute customer problem: Inspection and ERP live in separate worlds. Defect data in the camera, production data in SAP. No connection.

\subsection{SAP QM Connector}

\ruleitem{01}{Batch Traceability}{Every defect automatically linked to the SAP production order. Batch tracing in seconds instead of days.}
\ruleitem{02}{Supplier Scoring}{Defect rate per supplier, automatically calculated. Basis for data-driven supplier evaluation.}
\ruleitem{03}{Quality Analytics in ERP}{Dashboard directly in SAP: scrap rate, trends, costs. The quality manager never leaves their system.}

\subsection{Bosch ctrlX World: 1-Click Install}

The Bosch ctrlX platform is the ``App Store'' for industrial automation. 36ZERO as an app in ctrlX World = Product-Led Growth for Manufacturing.

\begin{highlightbox}
Strategic significance: ERP integration creates the strongest lock-in in B2B software. Once integrated into SAP, customers don't switch.
\end{highlightbox}

\clearpage
\section{Knowledge Base \&\\Workforce Shortage}
\ssubtitle{Digitize knowledge before it retires.}

\vspace{4pt}
\noindent\begin{minipage}[t]{0.32\linewidth}\centering\statcard{13--20M}{Retiring by 2036}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcard{30 Yrs}{Experience Lost}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcard{3 Days}{Knowledge Digitized}\end{minipage}

\begin{darkhighlight}
\textit{``Your best quality inspector retires in three years. We digitize their knowledge in three days.''}
\end{darkhighlight}

\subsection{Manufacturing Knowledge Base}

For every detected defect, the system searches an industry-specific knowledge base and automatically suggests root causes and solutions. Standards: IATF 16949, VDA 6.3/6.5, IPC-A-610, EU GMP, DIN EN ISO 5817.

\subsection{The Network Effect --- The True Moat}

\ruleitem{01}{Customers Contribute Anonymously}{Every solved cause-effect chain flows into the shared knowledge base.}
\ruleitem{02}{Database Gets Smarter With Every Customer}{Customer A solves crack problem \arrow{} helps customers B--Z automatically. Stack Overflow for manufacturing.}
\ruleitem{03}{Switching Cost Becomes Impossible}{Collective knowledge of 100+ manufacturers. Not a feature --- a moat.}

\begin{highlightbox}
Workflow: Expert + 36ZERO + 20 images \arrow{} model trained \arrow{} 30 years of experience digitized \arrow{} new employees benefit immediately.
\end{highlightbox}

\clearpage
\section{Competition \& New Markets}
\ssubtitle{The landscape --- and where the white spaces are.}

{\small
\begin{tabularx}{\linewidth}{@{}l l X X@{}}
\toprule
\textbf{Company} & \textbf{Revenue} & \textbf{Strength} & \textbf{Weakness} \\
\midrule
Cognex & \$1.34B & Market leader, Deep Learning & Hardware-locked, no SaaS \\
Keyence & \$7B & Sales strength & Proprietary, limited AI \\
Landing AI & \$57M raised & Andrew Ng, PLG & No Enterprise \\
Instrumental & --- & PCB expertise & Electronics only \\
Elementary & \$66M raised & Fast deployment & No Tier-1 customers \\
\bottomrule
\end{tabularx}
}

\subsection{The White Space}

\begin{minipage}[t]{0.48\linewidth}
\textbf{\color{primary}Autonomous Quality}\\
{\small Detect \arrow{} Diagnose \arrow{} Prescribe \arrow{} Act. No competitor goes beyond detection.}

\vspace{6pt}
\textbf{\color{primary}ERP-Native Intelligence}\\
{\small All are siloed solutions alongside ERP. Nobody delivers Quality Intelligence directly into SAP.}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\linewidth}
\textbf{\color{primary}Cross-Industry Knowledge}\\
{\small Nobody aggregates defect-cause-solution across customers and industries.}

\vspace{6pt}
\textbf{\color{primary}Knowledge Digitization}\\
{\small No platform positions itself as the solution to the workforce shortage.}
\end{minipage}

\subsection{New Markets}

{\small
\begin{tabularx}{\linewidth}{@{}l r X@{}}
\toprule
\textbf{Industry} & \textbf{Market} & \textbf{Opportunity} \\
\midrule
Pharma \& Medtech & \$5.7B+ & 3--5x pricing, compliance = must-have \\
Semiconductor & \$14.4B & Software layer open despite KLA dominance \\
Energy (Solar + Wind) & \$1.5B+ & Drone Inspection, 21.4\% CAGR \\
Infrastructure & \$34.4B & 40,000+ bridges, EU mandate \\
\bottomrule
\end{tabularx}
}

\clearpage
\section{Product Roadmap}
\ssubtitle{Four phases --- from prerequisite to paradigm shift.}

\ruleitem{\arrow}{Prerequisite: Vision --- Laying the Data Layer}{SAP QM Connector. 1-Click Install in Bosch ctrlX World. Pre-Trained Models per industry. Workforce shortage messaging.}
\ruleitem{P1}{Phase 1: Memory --- Building the Knowledge Base}{Process Parameter Correlation Engine. Manufacturing Knowledge Base v1 (IATF 16949, VDA, ISO). Auto-8D Reports. Pharma Module (GMP).}
\ruleitem{P2}{Phase 2: Autonomous Quality --- Closed Loop}{Agentic Quality: AI detects \arrow{} diagnoses \arrow{} corrects via ctrlX. Customer Knowledge Network. Self-Improving.}
\ruleitem{P3}{Phase 3: Manufacturing Quality OS}{Predictive Quality. Cross-Plant Benchmarking. Manufacturing GPT. Quality-as-a-Service for SMEs.}

\subsection{Top 3 Moves --- Immediately Actionable}

\ruleitem{{\color{darkgreen}01}}{ERP Integration + PLG via Marketplace}{Impact: High. Feasibility: High (partnerships exist). Solves the most acute problem with existing assets.}
\ruleitem{{\color{primary}02}}{Process Correlation Engine + Knowledge Base}{Impact: Very high (3--5x customer value, unique moat). Fundamentally differentiates from all competitors.}
\ruleitem{{\color{heading}03}}{Pharma / Regulated Industries Expansion}{3--5x higher prices, shorter sales cycle. Compliance = must-have = budget available.}

\clearpage
\section{The New Vision}
\ssubtitle{Six formulations --- from pragmatic to revolutionary.}

\begin{darkhighlight}
\textbf{\color{accent}Option A --- Autonomous Quality}\\[2pt]
{\color{white}\textit{``36ZERO makes quality control autonomous. Our AI detects defects, diagnoses root causes, and corrects processes --- without a human in the loop.''}}
\end{darkhighlight}

\begin{darkhighlight}
\textbf{\color{accent}Option B --- The Quality Intelligence Company}\\[2pt]
{\color{white}\textit{``We're building the intelligence layer for manufacturing quality. Inspection was the beginning. Today we deliver what's wrong --- why, and what to do about it.''}}
\end{darkhighlight}

\begin{darkhighlight}
\textbf{\color{accent}Option C --- Zero-Defect Manufacturing}\\[2pt]
{\color{white}\textit{``Zero defects. Not as a goal, but as a system. 36ZERO connects inspection with industry knowledge and autonomous correction.''}}
\end{darkhighlight}

\begin{darkhighlight}
\textbf{\color{accent}Option D --- Manufacturing Memory}\\[2pt]
{\color{white}\textit{``Machines don't forget. 36ZERO gives manufacturing a memory --- every defect, every cause, every solution.''}}
\end{darkhighlight}

\begin{darkhighlight}
\textbf{\color{accent}Option E --- Agentic Quality Platform}\\[2pt]
{\color{white}\textit{``The first AI platform with Quality Agents. Our agents see, understand, and act --- in seconds.''}}
\end{darkhighlight}

\begin{darkhighlight}
\textbf{\color{accent}Option F --- Self-Improving Quality Intelligence}\\[2pt]
{\color{white}\textit{``AI that improves while you produce. 36ZERO learns from every part and gets smarter with every customer.''}}
\end{darkhighlight}

\begin{highlightbox}
36ZERO has a choice: Remain a good inspection tool --- or become the platform for Autonomous Quality. The building blocks are there. Only the decision is missing.
\end{highlightbox}

\clearpage
\section{Market Potential: TAM, SAM, SOM}
\ssubtitle{From total market to addressable revenue potential.}

\vspace{4pt}
\noindent\begin{minipage}[t]{0.32\linewidth}\centering\statcard{\$41.7B}{TAM --- Machine Vision 2030}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcard{\$5.2B}{SAM --- AI Software Layer}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcard{\$120--350M}{SOM --- in 5 Years}\end{minipage}

\vspace{12pt}
\subsection{The Waterfall}

{\fontsize{11}{14}\selectfont
\noindent\textbf{\color{primary}TAM \$41.7B} --- Machine Vision Total Market 2030\\
{\color{bodytext}Cameras, optics, software, services. CAGR 13\%. \textit{Grand View Research}}

\noindent\textbf{\color{primary}SAM \$5.2B} --- AI Software Layer (12.5\% of TAM)\\
{\color{bodytext}Automotive 28\%, Electronics 19\%, Pharma 15\%. \textit{MarketsandMarkets}}

\noindent\textbf{\color{primary}SOM \$120--350M} --- Achievable in 5 Years\\
{\color{bodytext}DACH + EU core markets. 500--1,500 customers at €80--230K ACV.}
}

\vspace{6pt}

{\small
\begin{tabularx}{\linewidth}{@{}l r X@{}}
\toprule
\textbf{Industry} & \textbf{Share} & \textbf{36ZERO Fit} \\
\midrule
Automotive & 28\% & Very high --- Siemens, LEONI \\
Electronics/Semi & 19\% & High --- PCB, Wafer \\
Pharma/Medtech & 15\% & Very high --- 3--5x Pricing \\
Energy & 8\% & Medium --- Drone Inspection \\
Food \& Packaging & 12\% & Medium --- Commodity risk \\
\bottomrule
\end{tabularx}
}

\clearpage
\section{Competitive Deep Dive}
\ssubtitle{Feature matrix --- and where 36ZERO wins.}

{\footnotesize
\begin{tabularx}{\linewidth}{@{}l c c c c c@{}}
\toprule
\textbf{Feature} & \textbf{36ZERO} & \textbf{Cognex} & \textbf{Landing} & \textbf{Keyence} & \textbf{Elementary} \\
\midrule
Deep Learning & {\color{darkgreen}\checkmark{} 5--20} & {\color{darkgreen}\checkmark{} ViDi} & {\color{darkgreen}\checkmark{}} & {\color{darkyellow}Partial} & {\color{darkgreen}\checkmark{}} \\
Hardware & Agnostic & Proprietary & Agnostic & Proprietary & Own+3rd \\
ERP Integr. & {\color{darkgreen}\checkmark{} SAP} & No & No & No & No \\
Closed-Loop & Roadmap & No & No & No & No \\
Knowledge Base & Roadmap & No & No & No & No \\
Self-Improving & {\color{darkgreen}\checkmark{} Active} & No & {\color{darkyellow}Partial} & No & No \\
Pharma/GMP & Possible & {\color{darkgreen}\checkmark{}} & No & {\color{darkgreen}\checkmark{}} & No \\
Pricing & SaaS & HW+License & SaaS & HW+License & SaaS+HW \\
Tier-1 Customers & Siemens+ & Top-50 OEM & Mid-Market & Top-50 OEM & Scale-ups \\
\bottomrule
\end{tabularx}
}

\vspace{8pt}

\begin{darkhighlight}
36ZERO's unique advantage: No competitor combines ERP integration + Self-Improving AI + Closed-Loop roadmap. Hardware incumbents are locked in proprietary ecosystems. Software startups lack enterprise customers.
\end{darkhighlight}

\subsection{Strategic Implication}

\begin{minipage}[t]{0.48\linewidth}
\textbf{Against Cognex/Keyence}\\
{\small Don't compete on hardware. Software layer for any hardware. SaaS vs.\ licenses. PLG via SAP/Bosch Marketplace.}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\linewidth}
\textbf{Against Landing AI/Elementary}\\
{\small Enterprise references as moat. Siemens/Bosch = credibility. Vertical depth over horizontal.}
\end{minipage}

\clearpage
\section{Revenue Scenarios}
\ssubtitle{Three paths --- from status quo to Manufacturing Quality OS.}

{\small\textit{\color{subtitle}Scenarios based on market data and comparable SaaS companies. Precise projections require 36ZERO's internal KPIs.}}

\subsection{Scenario A: Status Quo --- ``Good Inspection Tool''}

\noindent\begin{minipage}[t]{0.32\linewidth}\centering\statcardred{€5--10M}{ARR in 3 Years}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcardred{€30--50K}{Avg.\ ACV}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcardred{High}{Commodity Risk}\end{minipage}

{\small\color{bodytext}Linear growth, feature competition. No moat. Commodity risk increases every year.}

\subsection{Scenario B: ERP + Pharma --- ``Quality Intelligence''}

\noindent\begin{minipage}[t]{0.32\linewidth}\centering\statcard{€15--30M}{ARR in 3 Years}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcard{€80--150K}{Avg.\ ACV}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcard{Medium}{Defensibility}\end{minipage}

{\small\color{bodytext}SAP Marketplace + Pharma. 3x ACVs. ERP lock-in. Achievable with existing team + 1--2 Pharma hires.}

\subsection{Scenario C: Full Platform --- ``Manufacturing Quality OS''}

\noindent\begin{minipage}[t]{0.32\linewidth}\centering\statcardgreen{€50--100M+}{ARR in 5 Years}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcardgreen{€150--300K}{Avg.\ ACV}\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}\centering\statcardgreen{Very High}{Defensibility}\end{minipage}

\begin{highlightbox}
Recommendation: Start Scenario B immediately, prepare Scenario C. Scenario A is not an option --- the market window for pure inspection closes in 18--24 months.
\end{highlightbox}

\clearpage
\section{Risk Analysis}
\ssubtitle{The 8 biggest strategic risks --- and how to address them.}

{\small
\begin{tabularx}{\linewidth}{@{}c l c c X@{}}
\toprule
\textbf{\#} & \textbf{Risk} & \textbf{Impact} & \textbf{Prob.} & \textbf{Mitigation} \\
\midrule
1 & Cognex: Autonomous Quality & {\color{darkred}Very High} & {\color{darkyellow}Medium} & Speed + ERP as moat. Pivot takes 2--3 yrs. \\
2 & Commoditization & {\color{darkred}Very High} & {\color{darkred}High} & Now: Knowledge Base + Closed-Loop. \\
3 & Foundation Models & {\color{darkyellow}High} & {\color{darkyellow}Medium} & Domain data = moat. VLMs need fine-tuning. \\
4 & AI Talent Shortage & {\color{darkyellow}High} & {\color{darkred}High} & Remote-first, university partnerships, equity. \\
5 & EU AI Act Delays & {\color{darkyellow}Medium} & {\color{darkyellow}Medium} & Compliance as feature and barrier. \\
6 & Customer Concentration & {\color{darkyellow}High} & {\color{darkyellow}Medium} & PLG via Marketplace. Max 15\% ARR. \\
7 & Long Sales Cycles & {\color{darkyellow}Medium} & {\color{darkred}High} & PLG: Self-Service, Land, Expand. \\
8 & Economic Downturn & {\color{darkyellow}High} & {\color{darkyellow}Medium} & ROI story: saves money. Payback {<}6 mo. \\
\bottomrule
\end{tabularx}
}

\begin{darkhighlight}
Most critical risk: \textbf{No.\ 2 --- Commoditization.} Every month without differentiation beyond inspection narrows the strategic window. The top 3 moves on the roadmap directly address this risk.
\end{darkhighlight}

\clearpage
\section{Sources \& References}
\ssubtitle{26 Tier-1 sources --- Research paper format.}

\begin{multicols}{2}
{\fontsize{8.5}{12}\selectfont\color{bodytext}
\noindent\textsuperscript{1} ASQ, ``Cost of Quality.'' COPQ: 15--20\%.\\[1pt]
\textsuperscript{2} McKinsey, ``Lighthouse Factories,'' Apr.~2024.\\[1pt]
\textsuperscript{3} Averroes.ai / IEEE, Medtech Case Study.\\[1pt]
\textsuperscript{4} SEMI, Industry Reports, 2024.\\[1pt]
\textsuperscript{5} Deloitte \& Manufacturing Inst., 2021/2024.\\[1pt]
\textsuperscript{6} German Federal Statistical Office / IAB.\\[1pt]
\textsuperscript{7} WEF, ``Future of Jobs,'' 2025.\\[1pt]
\textsuperscript{8} Grand View Research, MV Market, 2025.\\[1pt]
\textsuperscript{9} PwC, ``Sizing the Prize,'' AI Impact.\\[1pt]
\textsuperscript{10} Menlo Ventures, ``GenAI Report,'' 2025.\\[1pt]
\textsuperscript{11} MarketsandMarkets, Defect Detection.\\[1pt]
\textsuperscript{12} Gartner, AI Agents Forecast, Aug.~2025.\\[1pt]
\textsuperscript{13} McKinsey/WEF, Lighthouses, Apr.~2024.\\[1pt]
\textsuperscript{14} McKinsey, ``State of AI,'' Nov.~2025.\\[1pt]
\textsuperscript{15} NHTSA, 2024 Recall Report.\\[1pt]
\textsuperscript{16} GM, SEC Filings, 2024.\\[1pt]
\textsuperscript{17} Cognex, 10-K Filing, Feb.~2025.\\[1pt]
\textsuperscript{18} KLA Corporation, FY2024/25.\\[1pt]
\textsuperscript{19} SEMI, Fab Equipment Forecast, 2025.\\[1pt]
\textsuperscript{20} Deloitte, ``Smart Mfg Survey,'' 2025.\\[1pt]
\textsuperscript{21} Accenture, ``Reinventing Ops,'' 2024.\\[1pt]
\textsuperscript{22} FDA, PCCP, Dec.~2024.\\[1pt]
\textsuperscript{23} EU Commission, GMP Annex 22, Jul.~2025.\\[1pt]
\textsuperscript{24} Pharmaceutical Technology, Inspection.\\[1pt]
\textsuperscript{25} IISE, ``Cost of Quality,'' COPQ Study.\\[1pt]
\textsuperscript{26} NVIDIA, VLMs for Defects, Jan.~2026.
}
\end{multicols}

{\footnotesize\color{subtitle}All sources accessed and verified in January/February 2026.}

\vfill

\noindent\rule{\linewidth}{1.5pt}
\vspace{8pt}

\noindent\begin{minipage}[t]{0.5\linewidth}
{\fontsize{14}{18}\selectfont\bfseries\color{heading}Florian Ziesche}\\[3pt]
{\small\color{bodytext}florian@ainaryventures.com}\\
{\small\color{bodytext}+1 347 740 1465}
\end{minipage}\hfill
\begin{minipage}[t]{0.45\linewidth}\raggedleft
{\small\color{subtitle}Version 2.0 · February 2026}\\
{\footnotesize\color{subtitle}Confidential --- Not for distribution.}
\end{minipage}

\end{document}
