\documentclass[a4paper,11pt]{article}

\usepackage{fontspec}
\setmainfont{Helvetica Neue}[BoldFont=Helvetica Neue Bold, ItalicFont=Helvetica Neue Italic]
\usepackage[top=25mm, bottom=25mm, left=28mm, right=28mm]{geometry}
\usepackage{parskip}
\setlength{\parskip}{9pt}
\setlength{\parindent}{0pt}
\usepackage{xcolor}
\definecolor{navy}{HTML}{1B2A4A}
\definecolor{bodytext}{HTML}{2D3748}
\definecolor{subtle}{HTML}{718096}
\definecolor{linkblue}{HTML}{2563EB}
\definecolor{border}{HTML}{E2E8F0}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=linkblue, linkcolor=linkblue}
\usepackage{polyglossia}
\setdefaultlanguage{english}
\usepackage{microtype}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=14pt, itemsep=2pt, parsep=0pt, topsep=3pt, label={\textcolor{navy}{\textbullet}}}

\pagestyle{empty}
\color{bodytext}

\begin{document}

% === HEADER ===
\noindent{\fontsize{20}{24}\selectfont\bfseries\color{navy}Florian Ziesche}\\[2pt]
{\fontsize{9.5}{12}\selectfont\color{subtle}%
\href{mailto:florian@ziesche.co}{florian@ziesche.co}\enspace·\enspace+1\,347\,740\,1465\enspace·\enspace\href{https://linkedin.com/in/florian-ziesche-352b7249}{LinkedIn}\enspace·\enspace\href{https://github.com/fziescheus-alt}{GitHub}}

\vspace{8pt}
{\color{navy}\rule{\linewidth}{1.5pt}}
\vspace{10pt}

% === DATE + ADDRESSEE ===
{\fontsize{10}{13}\selectfont\color{subtle}February 6, 2026}

\vspace{1pt}
\noindent{\fontsize{11}{14}\selectfont\textbf{Bessemer Venture Partners Talent Team}\enspace---\enspace Associate / Senior Associate, AI}

\vspace{5pt}

% === BODY ===

Your State of AI report argues that this era will be defined not by a few Supernovas but by hundreds of Shooting Stars---vertical AI companies replacing labor budgets, not IT budgets. I agree. I spent five years building one.

As CEO and co-founder of 36ZERO Vision, I built a cloud computer vision platform for manufacturing quality inspection---exactly the kind of ``language-intensive workflow in an industry desperate for better tools'' your Vertical AI playbook describes. We sold to BMW, Siemens, Bosch, and Magna; grew total contract value 200\%+ to \$1.025M in a single year; and raised \texteuro5.5M across equity rounds and EU grants. When I read your thesis on AI Systems of Action replacing entrenched SoRs, I don't just understand it intellectually---I've lived the enterprise sales cycle, the integration pain, and the moment a plant manager realizes the AI actually works.

What I'd bring to Bessemer that most associate candidates cannot:

\begin{itemize}
  \item \textbf{Technical depth that survives diligence.} I built a RAG system with {<}0.2\% hallucination rate and production multi-agent architectures. My GitHub shows this in practice---\href{https://github.com/fziescheus-alt/CNC_Planner_PRO}{CNC\_Planner\_PRO} builds vertical AI for manufacturing costing, \href{https://github.com/fziescheus-alt/Exec-Research-Factory}{Exec-Research-Factory} generates decision-grade research with traceable evidence, and \href{https://github.com/fziescheus-alt/task-management}{task-management} is agentic AI built on Claude. When a founder pitches their architecture, I evaluate whether it holds at scale---or collapses under real data.

  \item \textbf{Operator pattern recognition.} I've been on both sides of the table: raising capital, managing a board, navigating a pivot, hiring engineers in competitive markets. I know what Q2T3 growth demands operationally---not from a spreadsheet, but from building the org that has to deliver it.

  \item \textbf{Sourcing edge in industrial AI.} My network spans German and European deep-tech founders building for manufacturing, automotive, and energy---verticals where Bessemer's ``Built World AI'' roadmap sees massive opportunity. These companies often reach \texteuro2--5M ARR before any US fund notices them.
\end{itemize}

I'm currently building Ainary Ventures through VC Lab (Decile Group, Cohort 6), which has sharpened my investment thesis on AI infrastructure and vertical applications. But my conviction is that the best way to back transformative AI companies is from inside a firm with Bessemer's depth of commitment---\$1B+ deployed to AI-native startups---and intellectual honesty. The Anti-Portfolio taught me more about your culture than any pitch deck could.

I'd welcome a conversation about how an operator who builds AI systems and sources deals others miss can strengthen Bessemer's AI practice.

\vspace{6pt}
\noindent Florian Ziesche

\end{document}
