\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage[top=0.8in, bottom=0.8in, left=0.8in, right=0.8in]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{hyperref}

% Try Helvetica Neue, fallback to Latin Modern
\IfFontExistsTF{Helvetica Neue}{
  \setmainfont{Helvetica Neue}
}{
  \setmainfont{Latin Modern Roman}
}

% Define accent color
\definecolor{accentgreen}{HTML}{00c96b}

% Remove page numbers
\pagestyle{empty}

% Reduce spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

% Header styling
\newcommand{\makeheader}{
  {\fontsize{18}{22}\selectfont\bfseries FLORIAN ZIESCHE}
  
  \vspace{2pt}
  {\color{accentgreen}\rule{\textwidth}{2pt}}
  
  \vspace{6pt}
  {\small New York, NY | +1 347 740 1465 | florian@ainaryventures.com}
  
  {\small linkedin.com/in/florian-ziesche | florianziesche.com | github.com/fziescheus-alt}
  
  \vspace{12pt}
}

\begin{document}

\makeheader

February 7, 2026

\vspace{6pt}

Dear Betaworks Team,

Your Spring 2026 Camp theme—Agent Systems—is exactly the technical frontier I've been building on. I recently architected a Legal AI platform using multi-agent RAG that achieved <0.2\% hallucination rate, which required solving precisely the challenges your Camp cohort companies will face: reliable agent orchestration, grounded retrieval, and production-grade agentic workflows that professionals actually trust.

Built and scaled AI SaaS to BMW, Siemens, and Bosch, raising €5.5M+. As MD/COO at 36ZERO Vision, I managed P\&L in a 150-person organization. My technical depth spans RAG systems, multi-agent architectures, CNC Planner Pro (production cost calculator validated against real ERP), and the Evolution Experiment (84 AI agents designing self-improvement protocols). I build AI systems—I don't just evaluate them. This includes my Legal AI work: built algorithms and system architecture (RAG, multi-agent) with Claude, research-driven with intent to commercialize but not current focus. It demonstrates applied AI depth.

What I'd bring to Betaworks is an operator who's built AI products in both vision and language, can do genuine technical diligence on agentic systems (not just ask about TAM), and has the founder empathy to support Camp companies through their hardest product decisions. I build in a week what others build in a month—because I work WITH AI, not just about it. Your portfolio—Hugging Face, Stability AI, and 150+ companies across your history—shows you value product velocity and pragmatic technical execution over theory.

I'm currently in VC Lab (Decile Group) building an AI-focused fund and based in NYC. I'd love to explore how I can contribute to your investment team and support the next generation of agent systems companies.

Best regards,

Florian Ziesche

\end{document}
