\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage[top=0.8in, bottom=0.8in, left=0.8in, right=0.8in]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{hyperref}

% Try Helvetica Neue, fallback to Latin Modern
\IfFontExistsTF{Helvetica Neue}{
  \setmainfont{Helvetica Neue}
}{
  \setmainfont{Latin Modern Roman}
}

% Define accent color
\definecolor{accentgreen}{HTML}{00c96b}

% Remove page numbers
\pagestyle{empty}

% Reduce spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

% Header styling
\newcommand{\makeheader}{
  {\fontsize{18}{22}\selectfont\bfseries FLORIAN ZIESCHE}
  
  \vspace{2pt}
  {\color{accentgreen}\rule{\textwidth}{2pt}}
  
  \vspace{6pt}
  {\small New York, NY | +1 347 740 1465 | florian@ainaryventures.com}
  
  {\small linkedin.com/in/florian-ziesche | florianziesche.com | github.com/fziescheus-alt}
  
  \vspace{12pt}
}

\begin{document}

\makeheader

February 7, 2026

\vspace{6pt}

Dear Bloomberg Beta Team,

You describe yourself as a fund with a ``speciality in machine intelligence.'' I don't just invest in that thesis—I live it every day. My current workflow involves multi-agent AI systems with autonomous planning, memory management, and proactive execution. Your portfolio—Flexport, Replit, Domino Data Lab, Codecademy—represents companies where machine intelligence transforms entire workflows, not just adds features.

Built and scaled AI SaaS to BMW, Siemens, and Bosch, raising €5.5M+. As MD/COO at 36ZERO Vision, I managed P\&L in a 150-person organization. My technical depth: RAG system achieving <0.2\% hallucination rate using hybrid retrieval (BM25 + semantic), cross-encoder re-ranking, and 4-agent verification pipelines. Multi-agent architectures, CNC Planner Pro (production cost calculator validated against real ERP), Evolution Experiment (84 AI agents designing self-improvement). I build AI systems—I don't just evaluate them. Legal AI: built algorithms and system architecture (RAG, multi-agent) with Claude, research-driven. I understand machine intelligence from the architecture layer up.

What I'd bring to Bloomberg Beta: Technical depth to evaluate ML/AI companies—I can read code, assess architectures, and spot the difference between a wrapper and a platform. Founder empathy—I've raised capital, hired teams, pivoted, and survived. Service mindset—my operator background means I default to ``how can I help?'' not ``where's my deal?'' Your emphasis on being ``low-ego, high-throughput people who founders want to be around'' resonates deeply. I build in a week what others build in a month—because I work WITH AI, not just about it.

I'm currently in VC Lab (Decile Group) building an AI-focused fund and NYC-based. I'd love to discuss how my builder background fits your team.

Best regards,

Florian Ziesche

\end{document}
