\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage[top=0.8in, bottom=0.8in, left=0.8in, right=0.8in]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{hyperref}

% Try Helvetica Neue, fallback to Latin Modern
\IfFontExistsTF{Helvetica Neue}{
  \setmainfont{Helvetica Neue}
}{
  \setmainfont{Latin Modern Roman}
}

% Define accent color
\definecolor{accentgreen}{HTML}{00c96b}

% Remove page numbers
\pagestyle{empty}

% Reduce spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

% Header styling
\newcommand{\makeheader}{
  {\fontsize{18}{22}\selectfont\bfseries FLORIAN ZIESCHE}
  
  \vspace{2pt}
  {\color{accentgreen}\rule{\textwidth}{2pt}}
  
  \vspace{6pt}
  {\small New York, NY | +1 347 740 1465 | f.ziesche.us@gmail.com}
  
  {\small linkedin.com/in/florian-ziesche | github.com/fziescheus-alt | github.com/fziescheus-alt}
  
  \vspace{12pt}
}

\begin{document}

\makeheader

February 7, 2026

\vspace{6pt}

Dear Conviction Team,

Conviction's thesis—that we are extremely early in translating powerful AI models into powerful products—mirrors exactly what I've spent the last several years doing as a founder and operator. Your portfolio's focus on companies where AI isn't a feature but the product itself—Harvey in legal AI, Cognition in software engineering, Cartesia in inference—represents the next generation of Software 3.0.

Built and scaled AI SaaS to BMW, Siemens, and Bosch, raising €5.0M+. As MD/COO at 36ZERO Vision, I managed P\&L in a 150-person organization navigating the gap between model capability and production-grade product. My technical depth: RAG system achieving <0.2\% hallucination rate, multi-agent architectures, CNC Planner Pro (production cost calculator validated against real ERP), Evolution Experiment (84 AI agents designing self-improvement). I build AI systems—I don't just evaluate them. My Legal AI work: built algorithms and system architecture (RAG, multi-agent) with Claude, research-driven—the kind of technical precision that separates real AI products from demos.

What excites me about Conviction is your values of technical depth plus operator judgment over financial modeling. I've lived both sides: as a founder navigating technical product decisions, and as a technical operator who understands why most AI products fail at the last mile of reliability. I build in a week what others build in a month—because I work WITH AI, not just about it.

I'm currently in VC Lab (Decile Group) refining my investment lens and based between NYC and Germany—a useful vantage point for evaluating the European AI ecosystem where Conviction already invests (Mistral, Listen Labs). I'd welcome the chance to discuss how my operator perspective and technical depth could strengthen your deal evaluation and portfolio support.

Best regards,

Florian Ziesche

\end{document}
