\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage[top=0.8in, bottom=0.8in, left=0.8in, right=0.8in]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{hyperref}

% Try Helvetica Neue, fallback to Latin Modern
\IfFontExistsTF{Helvetica Neue}{
  \setmainfont{Helvetica Neue}
}{
  \setmainfont{Latin Modern Roman}
}

% Define accent color
\definecolor{accentgreen}{HTML}{00c96b}

% Remove page numbers
\pagestyle{empty}

% Reduce spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

% Header styling
\newcommand{\makeheader}{
  {\fontsize{18}{22}\selectfont\bfseries FLORIAN ZIESCHE}
  
  \vspace{2pt}
  {\color{accentgreen}\rule{\textwidth}{2pt}}
  
  \vspace{6pt}
  {\small New York, NY | +1 347 740 1465 | florian@ainaryventures.com}
  
  {\small linkedin.com/in/florian-ziesche | florianziesche.com | github.com/fziescheus-alt}
  
  \vspace{12pt}
}

\begin{document}

\makeheader

February 7, 2026

\vspace{6pt}

Dear FirstMark Team,

FirstMark's community-driven approach to venture—from your Data Driven NYC events to the deep enterprise networks you've built over 15+ years—is exactly the kind of platform where my operator background can compound. Your iconic NYC portfolio (Pinterest, Shopify, Discord, DraftKings) and strong AI thesis, particularly with David Waltcher's recent promotion to Partner focusing on dev tools, AI, and infrastructure, signals where FirstMark is doubling down.

Built and scaled AI SaaS to BMW, Siemens, and Bosch, raising €5.5M+. As MD/COO at 36ZERO Vision, I built B2B SaaS enterprise go-to-market from zero in Munich's tech ecosystem within a 150-person organization. My technical depth: RAG system achieving <0.2\% hallucination rate using multi-agent architecture, CNC Planner Pro (production cost calculator validated against real ERP), Evolution Experiment (84 AI agents designing self-improvement). I build AI systems—I don't just evaluate them. Legal AI: built algorithms and system architecture (RAG, multi-agent) with Claude, research-driven. Having built production AI systems that enterprises actually trusted, I know the difference between an impressive model and a deployable product.

What I'd bring to FirstMark: Application software intuition from building, selling, and scaling B2B SaaS. AI architecture fluency—I can evaluate technical moats, data flywheels, and model strategies rapidly. Founder empathy—when a portfolio company CEO calls with a problem, I've been in their exact position. I build in a week what others build in a month—because I work WITH AI, not just about it. I bring a European founder network that complements your portfolio's global ambitions.

I'm currently in VC Lab (Decile Group) building an AI-focused fund and based in NYC. I'd love to contribute to FirstMark's next chapter of AI investing.

Best regards,

Florian Ziesche

\end{document}
