\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage[top=0.8in, bottom=0.8in, left=0.8in, right=0.8in]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{hyperref}

% Try Helvetica Neue, fallback to Latin Modern
\IfFontExistsTF{Helvetica Neue}{
  \setmainfont{Helvetica Neue}
}{
  \setmainfont{Latin Modern Roman}
}

% Define accent color
\definecolor{accentgreen}{HTML}{00c96b}

% Remove page numbers
\pagestyle{empty}

% Reduce spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

% Header styling
\newcommand{\makeheader}{
  {\fontsize{18}{22}\selectfont\bfseries FLORIAN ZIESCHE}
  
  \vspace{2pt}
  {\color{accentgreen}\rule{\textwidth}{2pt}}
  
  \vspace{6pt}
  {\small New York, NY | +1 347 740 1465 | f.ziesche.us@gmail.com}
  
  {\small linkedin.com/in/florian-ziesche | github.com/fziescheus-alt | github.com/fziescheus-alt}
  
  \vspace{12pt}
}

\begin{document}

\makeheader

February 7, 2026

\vspace{6pt}

Dear General Catalyst Team,

General Catalyst's investment in companies like Stripe, Airbnb, Snap, and Instacart demonstrates a fund that backs category-defining companies at growth stage—companies that transform entire industries through technology. Your increasing focus on AI infrastructure and enterprise applications, particularly with \$8B+ AUM, positions you at the intersection of capital scale and technical conviction.

Built and scaled AI SaaS to BMW, Siemens, and Bosch, raising €5.5M+. As MD/COO at 36ZERO Vision, I managed P\&L and operations in a 150-person organization, navigating the journey from early-stage product to enterprise-scale deployment. My technical depth: RAG system achieving <0.2\% hallucination rate through multi-agent coordination, CNC Planner Pro (production cost calculator validated against real ERP systems), Evolution Experiment (84 AI agents designing self-improvement protocols). I build AI systems—I don't just evaluate them. Legal AI: built algorithms and system architecture (RAG, multi-agent) with Claude, research-driven. This technical foundation allows me to evaluate AI companies at the architecture level.

What I'd bring to General Catalyst: Operator perspective on scaling AI companies from seed through growth stages—I've lived the challenges of enterprise sales, technical architecture decisions, and organizational scaling. Technical fluency to evaluate AI moats and data flywheels. European network that complements your global portfolio strategy. I build in a week what others build in a month—because I work WITH AI, not just about it.

I'm currently in VC Lab (Decile Group) building an AI-focused fund and based in NYC. General Catalyst's combination of growth-stage capital with technical depth makes it a unique platform for supporting the next generation of AI companies. I'd welcome the opportunity to discuss how my operator-builder background can contribute to your investment process.

Best regards,

Florian Ziesche

\end{document}
