\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage[top=0.8in, bottom=0.8in, left=0.8in, right=0.8in]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{hyperref}

\IfFontExistsTF{Helvetica Neue}{
  \setmainfont{Helvetica Neue}
}{
  \setmainfont{Latin Modern Roman}
}

\definecolor{accentgreen}{HTML}{00c96b}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

\newcommand{\makeheader}{
  {\fontsize{18}{22}\selectfont\bfseries FLORIAN ZIESCHE}
  
  \vspace{2pt}
  {\color{accentgreen}\rule{\textwidth}{2pt}}
  
  \vspace{6pt}
  {\small New York, NY | +1 347 740 1465 | f.ziesche.us@gmail.com}
  
  {\small linkedin.com/in/florian-ziesche | github.com/fziescheus-alt}
  
  \vspace{12pt}
}

\begin{document}

\makeheader

February 7, 2026

\vspace{6pt}

Dear HOF Capital Team,

I saw your Associate and Senior Associate roles and wanted to reach out. HOF Capital's focus on AI-native companies and your investments in OpenAI, Anthropic, and xAI tell me you take technical depth seriously — not just the hype cycle. That's exactly the kind of fund I want to work at.

I'm not a finance person who got interested in AI. I spent five years building an AI startup from nothing — demos, MVPs, product-market fit, sales from zero to over \$1M in revenue. I raised \texteuro5.5M across angel and VC rounds, sat in hundreds of meetings with funds, hired a team of 15, fired people, ran out of money, and kept going. I went through Alchemist Accelerator and multiple programs in Germany and the U.S.

That journey is what I bring. I can read founders because I was one. I know who's delusional in a good way and who's delusional in a dangerous way — because I've been both. I have an existing network of angels, VCs, and founders who trust me because I did the work, not because I wrote a check.

I don't just talk about AI — I'm obsessed with it. I build production RAG systems, multi-agent architectures, and open-source tools. I speak the language of both startups and venture capital, which is rarer than people think.

I'm also a bridge between two markets. German-born, built companies in Munich, now in New York. European and international founders don't have many investors who understand both sides. I do, and they know it.

Happy to share more or jump on a call whenever works for you.

\vspace{6pt}
\noindent Florian Ziesche

\end{document}
