\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage[top=0.8in, bottom=0.8in, left=0.8in, right=0.8in]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{hyperref}

% Try Helvetica Neue, fallback to Latin Modern
\IfFontExistsTF{Helvetica Neue}{
  \setmainfont{Helvetica Neue}
}{
  \setmainfont{Latin Modern Roman}
}

% Define accent color
\definecolor{accentgreen}{HTML}{00c96b}

% Remove page numbers
\pagestyle{empty}

% Reduce spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

% Header styling
\newcommand{\makeheader}{
  {\fontsize{18}{22}\selectfont\bfseries FLORIAN ZIESCHE}
  
  \vspace{2pt}
  {\color{accentgreen}\rule{\textwidth}{2pt}}
  
  \vspace{6pt}
  {\small New York, NY | +1 347 740 1465 | f.ziesche.us@gmail.com}
  
  {\small linkedin.com/in/florian-ziesche | github.com/fziescheus-alt | github.com/fziescheus-alt}
  
  \vspace{12pt}
}

\begin{document}

\makeheader

February 7, 2026

\vspace{6pt}

Dear Lux Capital Team,

Your recent piece on NYC's AI opportunity and the ``Great Talent Dividend'' resonated deeply—I'm one of those operators making the deliberate move from building AI companies to investing in them. Your portfolio spans from Runway and Hugging Face to Together AI and Physical Intelligence—the full AI stack from foundational models to embodied intelligence.

Built and scaled AI SaaS to BMW, Siemens, and Bosch, raising €5.0M+. As MD/COO at 36ZERO Vision, I navigated the full journey from technical prototype to enterprise customers in a 150-person organization. My technical depth: RAG system achieving <0.2\% hallucination rate through multi-agent coordination—the kind of reliability bar your portfolio companies know is the difference between a research project and a business. Multi-agent architectures, CNC Planner Pro (production cost calculator validated against real ERP), Evolution Experiment (84 AI agents designing self-improvement). I build AI systems—I don't just evaluate them. Legal AI: built algorithms and system architecture (RAG, multi-agent) with Claude, research-driven.

What draws me to Lux specifically is your conviction that the best AI investments require deep technical understanding, not just pattern matching on metrics. With over \$5B AUM, you're investing across layers I've built across: computer vision at the perception level, LLMs and agents at the reasoning level, and enterprise deployment at the product level. I build in a week what others build in a month—because I work WITH AI, not just about it.

I'm currently in VC Lab (Decile Group) building an AI-focused fund, based between NYC and Germany, and bring a European network that complements Lux's growing transatlantic portfolio (Sakana AI, Mistral). I'd welcome the opportunity to discuss how my technical depth and operator experience can add value to your investment process.

Best regards,

Florian Ziesche

\end{document}
