\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage[top=0.8in, bottom=0.8in, left=0.8in, right=0.8in]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{hyperref}

% Try Helvetica Neue, fallback to Latin Modern
\IfFontExistsTF{Helvetica Neue}{
  \setmainfont{Helvetica Neue}
}{
  \setmainfont{Latin Modern Roman}
}

% Define accent color
\definecolor{accentgreen}{HTML}{00c96b}

% Remove page numbers
\pagestyle{empty}

% Reduce spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

% Header styling
\newcommand{\makeheader}{
  {\fontsize{18}{22}\selectfont\bfseries FLORIAN ZIESCHE}
  
  \vspace{2pt}
  {\color{accentgreen}\rule{\textwidth}{2pt}}
  
  \vspace{6pt}
  {\small New York, NY | +1 347 740 1465 | f.ziesche.us@gmail.com}
  
  {\small linkedin.com/in/florian-ziesche | github.com/fziescheus-alt | github.com/fziescheus-alt}
  
  \vspace{12pt}
}

\begin{document}

\makeheader

February 7, 2026

\vspace{6pt}

Dear Lionheart Ventures Team,

Your thesis around ``the wise development of transformative technologies'' isn't just investment framing—it's a design philosophy I've been building toward for years. Your investments in Anthropic's safety-first approach, Goodfire's interpretability tools, and Gray Swan's AI safety testing reflect the conviction that the companies winning the next decade will be those that build AI systems humans can understand, audit, and trust.

Built and scaled AI SaaS to BMW, Siemens, and Bosch, raising €5.5M+. As MD/COO at 36ZERO Vision, I managed P\&L in a 150-person organization. When I built a production RAG system achieving <0.2\% hallucination rates, the goal wasn't just technical performance—it was ensuring AI delivers trustworthy outputs that humans can rely on and verify. My technical depth: RAG systems, multi-agent architectures, CNC Planner Pro (production cost calculator validated against real ERP), and the Evolution Experiment (84 AI agents designing self-improvement). I build AI systems—I don't just evaluate them. This includes Legal AI: built algorithms and system architecture (RAG, multi-agent) with Claude, research-driven with intent to commercialize but not current focus.

What I bring to Lionheart: You're the rare fund where evaluating Softmax's compute optimization or Piramidal's AI architecture requires genuine technical depth. I can read codebases, assess model architectures, and distinguish frontier research from marketing—while connecting it to the human agency thesis that makes your fund differentiated. I build in a week what others build in a month—because I work WITH AI, not just about it.

I'm currently in VC Lab (Decile Group) building an AI-focused fund and based in NYC. I'd welcome a conversation about how my builder-operator perspective fits your team.

Best regards,

Florian Ziesche

\end{document}
