\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage[top=0.8in, bottom=0.8in, left=0.8in, right=0.8in]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{hyperref}

% Try Helvetica Neue, fallback to Latin Modern
\IfFontExistsTF{Helvetica Neue}{
  \setmainfont{Helvetica Neue}
}{
  \setmainfont{Latin Modern Roman}
}

% Define accent color
\definecolor{accentgreen}{HTML}{00c96b}

% Remove page numbers
\pagestyle{empty}

% Reduce spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

% Header styling
\newcommand{\makeheader}{
  {\fontsize{18}{22}\selectfont\bfseries FLORIAN ZIESCHE}
  
  \vspace{2pt}
  {\color{accentgreen}\rule{\textwidth}{2pt}}
  
  \vspace{6pt}
  {\small New York, NY | +1 347 740 1465 | f.ziesche.us@gmail.com}
  
  {\small linkedin.com/in/florian-ziesche | github.com/fziescheus-alt | github.com/fziescheus-alt}
  
  \vspace{12pt}
}

\begin{document}

\makeheader

February 7, 2026

\vspace{6pt}

Dear Point72 Ventures Team,

Point72 Ventures occupies a unique position—a firm backed by Steven A. Cohen's decades of data-driven public markets experience, applying that rigor to early-stage AI and enterprise investing. Your portfolio of 130+ investments spanning fintech, AI, and deep tech—from Adonis in healthcare AI to Apex in space manufacturing to Anvilogic in cybersecurity—shows pattern recognition across industries. That's exactly the lens I'd bring from the operator side.

Built and scaled AI SaaS to BMW, Siemens, and Bosch, raising €5.0M+. As MD/COO at 36ZERO Vision, I owned the P\&L and operations in a 150-person organization—the kind of data-driven execution Point72 values. My technical depth: RAG system achieving <0.2\% hallucination rate, multi-agent architectures, CNC Planner Pro (production cost calculator validated against real ERP), Evolution Experiment (84 AI agents designing self-improvement). I build AI systems—I don't just evaluate them. Legal AI: built algorithms and system architecture (RAG, multi-agent) with Claude, research-driven. I write code, deploy models, and stress-test architectures.

What I'd bring to P72V: Technical sourcing edge—I can identify breakout AI companies before they hit mainstream VC radar because I understand the technology at the architecture level. Enterprise sales lens—having sold AI to BMW and Siemens, I can evaluate whether a startup's enterprise motion is real or aspirational. Quantitative rigor—my TUM education (Corporate Finance + Data Science/ML) means I model companies with discipline. I build in a week what others build in a month—because I work WITH AI, not just about it.

I'm currently in VC Lab (Decile Group) building an AI-focused fund and based in NYC. Point72's bridge between public market sophistication and venture investing is a model I deeply respect. I'd love to bring my operator-builder perspective to your AI investing practice.

Best regards,

Florian Ziesche

\end{document}
