\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage[top=0.8in, bottom=0.8in, left=0.8in, right=0.8in]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{hyperref}

% Try Helvetica Neue, fallback to Latin Modern
\IfFontExistsTF{Helvetica Neue}{
  \setmainfont{Helvetica Neue}
}{
  \setmainfont{Latin Modern Roman}
}

% Define accent color
\definecolor{accentgreen}{HTML}{00c96b}

% Remove page numbers
\pagestyle{empty}

% Reduce spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

% Header styling
\newcommand{\makeheader}{
  {\fontsize{18}{22}\selectfont\bfseries FLORIAN ZIESCHE}
  
  \vspace{2pt}
  {\color{accentgreen}\rule{\textwidth}{2pt}}
  
  \vspace{6pt}
  {\small New York, NY | +1 347 740 1465 | f.ziesche.us@gmail.com}
  
  {\small linkedin.com/in/florian-ziesche | github.com/fziescheus-alt}
  
  \vspace{12pt}
}

\begin{document}

\makeheader

February 9, 2026

\vspace{6pt}

Dear Andrew,

Your LinkedIn post stopped my scroll — not because of the title, but because of the phrase ``actually dig in.'' That's rare. Most associate roles are glorified model-updating positions. Wingspan's role sounds like building a firm, not just working inside one. That's the only kind of role I'm interested in.

Here's why I'd be effective on day one:

\textbf{I've been on both sides of the table.} As CEO of 36ZERO Vision, I raised \texteuro5.5M+ from institutional VCs and angels, managed P\&L in a 150-person organization, and sold enterprise AI to BMW, Siemens, and Bosch. I know what diligence looks like from the founder's seat — the questions that matter, the ones that waste time, and the signals that don't show up in a data room.

\textbf{I can go deep on research, not just summarize it.} I recently built a Legal AI platform with multi-agent architecture achieving <0.2\% hallucination rates. Before that, cloud computer vision systems processing industrial data in real-time. When I research an investment thesis or a niche market, I don't stop at the pitch deck — I understand the technical moats, the operational risks, and where the value actually compounds.

\textbf{Wingspan's niche strategy resonates with how I think.} You look for simple, proven business models in overlooked markets — ``alternatives to alternatives.'' I've spent the last two months researching exactly this pattern: undercapitalized niches where AI creates 10x operational leverage. Manufacturing, legal, municipal government — markets where expertise is scarce, data is trapped, and incumbents are paralyzed. I'd bring that lens to your sourcing immediately.

\textbf{I can shape your internal tech stack.} I'm not an associate who needs to Google ``what is an API.'' I've built production AI systems, automated investment research workflows, and designed multi-agent architectures. If Wingspan wants to use technology as an edge in sourcing and diligence — I can build that, not just spec it.

I'm currently in VC Lab (Decile Group) and based in NYC. I'd welcome 20 minutes to discuss how my operator background and technical depth could accelerate Wingspan's next chapter.

\vspace{12pt}

Warm regards,

\vspace{4pt}

Florian Ziesche

\end{document}
