%!TEX program = xelatex
\documentclass[11pt,letterpaper]{article}

% ─── Geometry ───────────────────────────────────────────────
\usepackage[top=0.85in, bottom=0.75in, left=1.0in, right=1.0in]{geometry}

% ─── Fonts ──────────────────────────────────────────────────
\usepackage{fontspec}
\setmainfont{Helvetica Neue}[
  UprightFont = *,
  BoldFont = * Bold,
  ItalicFont = * Italic,
  BoldItalicFont = * Bold Italic
]

% ─── Packages ───────────────────────────────────────────────
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}

% ─── Colors ─────────────────────────────────────────────────
\definecolor{darkblue}{HTML}{1a1a2e}
\definecolor{accent}{HTML}{2d3436}
\definecolor{linkblue}{HTML}{1e3a5f}

% ─── Hyperref ───────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  linkcolor=linkblue,
  urlcolor=linkblue,
  pdfauthor={Florian Ziesche},
  pdftitle={Cover Letter — D.E. Shaw Group, Entrepreneur in Residence}
}

% ─── Spacing ────────────────────────────────────────────────
\setlength{\parskip}{5.5pt}
\setlength{\parindent}{0pt}
\pagestyle{empty}

\begin{document}

% ─── Header ─────────────────────────────────────────────────
\begin{center}
{\Large\bfseries\color{darkblue} FLORIAN ZIESCHE}\\[3pt]
{\small
550 10th Ave, New York, NY 10018\enspace$\cdot$\enspace
347.740.1465\enspace$\cdot$\enspace
\href{mailto:florian@ziesche.co}{florian@ziesche.co}\\[1pt]
\href{https://www.linkedin.com/in/florian-ziesche-352b7249/}{LinkedIn}\enspace$\cdot$\enspace
\href{https://github.com/fziescheus-alt}{GitHub}
}
\end{center}

\vspace{4pt}
\noindent\rule{\textwidth}{0.4pt}
\vspace{2pt}

% ─── Date & Addressee ──────────────────────────────────────
\noindent February 6, 2026

\noindent DESCOvery — Venture Studio\\
The D.~E.~Shaw Group\\
1166 Avenue of the Americas\\
New York, NY 10036

\noindent\textbf{Re: Entrepreneur in Residence — DESCOvery}

% ─── Body ───────────────────────────────────────────────────

DESCOvery's model is rare: pair a builder's autonomy with the quantitative infrastructure and capital depth of the D.~E.~Shaw group to create ventures that wouldn't otherwise exist. That combination is precisely why I'm writing. I've spent the last five years building technology companies from zero—raising capital, shipping production AI to Fortune~500 enterprises, and scaling revenue against real constraints. I'd like to do it again, inside DESCOvery, at a higher order of magnitude.

\textbf{Proven 0-to-1 Track Record.}\enspace
As CEO \& Founder of 36ZERO Vision, I built a cloud computer-vision SaaS platform from a blank repo to enterprise contracts with BMW, Siemens, Bosch, Magna, and Linamar. I raised €3M in equity, secured an additional €2.5M (grants + operational round), and grew total contract value 200\%+ to \$1.025M within a single year. As MD/COO, I managed the P\&L for a 150-person organization. These aren't paper plans—they're production systems serving automotive OEMs in regulated environments.

\textbf{Technical Depth That Ships.}\enspace
I build production AI, not prototypes that languish in notebooks. My work includes a RAG system operating at a ${<}$0.2\% hallucination rate, agentic AI workflows, and multi-agent architectures deployed at scale. My public GitHub reflects how I build: \href{https://github.com/fziescheus-alt/CNC_Planner_PRO}{\texttt{CNC\_Planner\_PRO}}—a full manufacturing cost calculator built from scratch in days, not months; \href{https://github.com/fziescheus-alt}{\texttt{Exec-Research-Factory}}—decision-grade executive research tooling that mirrors the analytical rigor D.~E.~Shaw is known for; and \href{https://github.com/fziescheus-alt}{\texttt{nexus-outcome-engine}}—a TypeScript system for quantitative outcome tracking. I prototype fast, validate with data, and kill what doesn't work.

\textbf{Quantitative Foundation.}\enspace
My M.Sc.\ and B.Sc.\ from TU Munich span Corporate Finance, Data Science, and Machine Learning—a deliberate intersection. I think in unit economics, expected value, and marginal returns, not feature lists. Currently, I'm building Ainary Ventures through Decile Group's VC Lab (Cohort~6), evaluating AI-native investment theses with the same quantitative discipline that defines D.~E.~Shaw's culture.

\textbf{Where I'd Build Inside DESCOvery.}\enspace
Two opportunity spaces excite me at the intersection of AI and DESCOvery's focus areas:
\begin{itemize}[nosep, leftmargin=1.2em, topsep=2pt]
\item \textbf{AI-native financial data infrastructure}—using multi-agent systems to transform unstructured alternative data (contracts, filings, sensor feeds) into structured, decision-grade signals for institutional capital allocators. The tooling I've already built (\texttt{Exec-Research-Factory}, \texttt{research-system}) is a working prototype of this thesis.
\item \textbf{Autonomous underwriting for specialty insurance}—combining computer vision (my domain) with LLM-driven document analysis to price complex commercial risks in minutes rather than weeks, targeting the \$80B+ specialty lines market.
\end{itemize}

Both leverage D.~E.~Shaw's data infrastructure and quantitative expertise in ways no standalone founder could replicate. That's the entire point of DESCOvery—and the reason I'm not applying to an accelerator.

I'm not looking for permission to be entrepreneurial. I've already done it. What I'm offering is a builder who ships fast, thinks quantitatively, and has a track record of turning ambiguity into enterprise revenue—paired with the unique resources DESCOvery provides.

I would welcome the opportunity to discuss how my experience maps to the ventures you're exploring.

\vspace{10pt}
\noindent Florian Ziesche

\end{document}
